### 2016-12-23 README.Rmd
update docs

`r Biocpkg("MSnbase")` is an R/Bioconductor package that provides
infrastructure for plotting, data manipulation and processing of
MS-based proteomics data. The project was started by
[Laurent Gatto](http://lgatto.github.io/) in October 2010 (Mon Oct 4
23:35:23 2010, according to the git log) and has, since then,
benefited from
[various contributions](http://lgatto.github.io/msnbase-contribs/).

>>>>

[**MSbase**](http://lgatto.github.io/MSnbase/) is an R/Bioconductor
package that provides infrastructure for plotting, data manipulation
and processing of mass spectrometry and proteomics data. The project
was started by [Laurent Gatto](http://lgatto.github.io/) in October
2010 (Mon Oct 4 23:35:23 2010, according to the git log) and has,
since then, benefited from
[various contributions](http://lgatto.github.io/msnbase-contribs/).
